### 2016-11-03 capability-machine.tex
Changed the recursive domain equation to be recursive in the worlds

\newcommand{\Rel}{\plaindom{Rel}}
\newcommand{\States}{\plaindom{State}}
\newcommand{\RegionNames}{\plaindom{RegionName}}
\newcommand{\Regions}{\plaindom{Region}}
\newcommand{\Reg}{\plaindom{Reg}}
\newcommand{\Regwk}{\Reg_{\futurewk}}
\newcommand{\Regstr}{\Reg_{\futurestr}}
\newcommand{\Worlds}{\plaindom{World}}
\newcommand{\Wor}{\plaindom{Wor}}
\newcommand{\StorePred}{\plaindom{HeapSegPred}}
\newcommand{\UPred}[1]{\plaindom{UPred}(#1)}
\newcommand{\DCPred}[1]{\plaindom{P}^\downarrow(#1)}

@@

\section{Logical Relation'}
\subsection{Worlds}
Assume $\Regstr$ and $\Regwk$ are preordered \cofes{} and $\xi_{\var{wk}}$ and $\xi_{\var{str}}$ are isomorphisms such that
\begin{align*}
  \xi_{\var{wk}} :   \Regwk \cong \blater (&\{\revoked\} \union \\
                                           & \{\temp\} \times \States \times \Rel \times (\States \fun ((\nats \finparfun \Regwk) \monnefun \UPred{\HeapSegments})) \union \\
                                           & \{\perma\} \times \States \times \Rel \times (\States \fun ((\nats \finparfun \Regstr) \monnefun \UPred{\HeapSegments})))_{\future_{\var{wk}}} \\ \\
  \xi_{\var{str}} :   \Regstr \cong \blater (&\{\revoked\} \union \\
                                           & \{\temp\} \times \States \times \Rel \times (\States \fun ((\nats \finparfun \Regwk) \monnefun \UPred{\HeapSegments})) \union \\
                                           & \{\perma\} \times \States \times \Rel \times (\States \fun ((\nats \finparfun \Regstr) \monnefun \UPred{\HeapSegments})))_{\future_{\var{str}}}
\end{align*}
We now define the regions to be
\begin{align*}
  \Regions = & \{\revoked\} \union \\
             & \{\temp\} \times \States \times \Rel \times (\States \fun ((\nats \finparfun \Regwk) \monnefun \UPred{\HeapSegments})) \union \\
             & \{\perma\} \times \States \times \Rel \times (\States \fun ((\nats \finparfun \Regstr) \monnefun \UPred{\HeapSegments}))
\end{align*}
And the worlds are
\[
  \Worlds = \RegionNames \finparfun \Regions
\]
Where $\RegionNames = \nats$.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,(\start,\addrend),=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun ((\nats \finparfun \Regwk) \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; (\start,\addrend) \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\hat{W})
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,(\start,\addrend),=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun ((\nats \finparfun \Regstr) \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\hat{W}})
    \end{aligned}
  \right\}
\end{align*}
\lau{In the above $H$ definitions, $\hat{W}$ is not a world, so there is a type problem that needs to be fixed. Maybe solve the recursive domain equations wrt the worlds instead.}

>>>>

\newcommand{\Rel}{\plaindom{Rel}}
\newcommand{\States}{\plaindom{State}}
\newcommand{\RegionNames}{\plaindom{RegionName}}
\newcommand{\Regions}{\plaindom{Region}}
\newcommand{\Reg}{\plaindom{Reg}}
\newcommand{\Worlds}{\plaindom{World}}
\newcommand{\Wor}{\plaindom{Wor}}
\newcommand{\Worwk}{\Wor_{\futurewk}}
\newcommand{\Worstr}{\Wor_{\futurestr}}
\newcommand{\xiwk}{\xi_{\var{wk}}}
\newcommand{\xistr}{\xi_{\var{str}}}
\newcommand{\StorePred}{\plaindom{HeapSegPred}}
\newcommand{\UPred}[1]{\plaindom{UPred}(#1)}
\newcommand{\DCPred}[1]{\plaindom{P}^\downarrow(#1)}

@@

\section{Logical Relation'}
\subsection{Worlds}
Assume $\Worstr$ and $\Worwk$ are preordered \cofes{} and $\xi_{\var{wk}}$ and $\xi_{\var{str}}$ are isomorphisms such that
\begin{align*}
  \xi_{\var{wk}} :   \Worwk \cong \blater (\nats \finparfun (&\{\revoked\} \union \\
                                           & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \union \\
                                           & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{wk}}}) \\ \\
  \xi_{\var{str}} :   \Worstr \cong (\nats \finparfun \blater (&\{\revoked\} \union \\
                                           & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \union \\
                                           & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{str}}})
\end{align*}
We now define the regions to be
\begin{align*}
  \Regions = & \{\revoked\} \union \\
             & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \union \\
             & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments}))
\end{align*}
And the worlds are
\[
  \Worlds = \RegionNames \finparfun \Regions
\]
Where $\RegionNames = \nats$.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,(\start,\addrend),=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; (\start,\addrend) \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,(\start,\addrend),=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}
\lau{In the above $H$ definitions, $\hat{W}$ is not a world, so there is a type problem that needs to be fixed. Maybe solve the recursive domain equations wrt the worlds instead.}
